%%%------------------------------------------------------------------------------%%%
%%% Preface %%% 
%%%------------------------------------------------------------------------------%%%

\underline{\textbf{\LARGE{Preface}}}\\[2cm]
This lecture will give you a brief introduction to so what is called 'Big Data'. We will quickly refresh the basics about databases, data models and data processing you have learned so far and compare those to the distributed world of Big Data. \\
After that we will take a deep dive into the foundations of distributed data storages and data processing as well as the belonging concepts of reliability, scalability, replication, partitioning, batch and stream processing. \\
Later on we will take a look at the most common used software and frameworks (mostly the hadoop ecosystem). \\
At the end, as you know the basic concepts and you are able to setup and work with distributed environments and huge data sets, there will be a short introduction to data science. \\

At the end of each lesson, there will be some hands-on exercises, which we will start together and which have to be finished till the next week.
This lecture will only be about 36 hours in 12 weeks (1 slot each week), which is very little time to cover such an extensive topic. So pay close attention and if you can't keep up, feel free to ask questions at the end of each lesson. \\

You can find:
\begin{samepage}
\begin{itemize}
	\item this \textbf{script} (and \LaTeX{}-sources),
	\item \textbf{slides} presented within the lecture,
	\item \textbf{excercises} and \textbf{solutions},
	\item \textbf{docker images}, \textbf{scripts} as well as \textbf{sample data sets}
\end{itemize}
\end{samepage}
here:
\begin{lstlisting}[language=bash,frame=none,numbers=none,xleftmargin=0.05\textwidth,xrightmargin=0.05\textwidth]
 https://github.com/marcelmittelstaedt/BigData
\end{lstlisting}

You can just download everything directly or install \lstinline{git} and get everything by using:
\begin{lstlisting}[language=bash,frame=none,numbers=none,xleftmargin=0.05\textwidth,xrightmargin=0.05\textwidth]
 git clone https://github.com/marcelmittelstaedt/BigData.git
\end{lstlisting}
and 
\begin{lstlisting}[language=bash,frame=none,numbers=none,xleftmargin=0.05\textwidth,xrightmargin=0.05\textwidth]
 git pull
\end{lstlisting}
to get the most recent version.\\

If you find any mistakes or misspellings feel free to send me a mail\\
(\textbf{\href{mailto:mittelstaedtmarcel@googlemail.com}{mittelstaedtmarcel@googlemail.com}})
or if you are able to, commit a push request.\\

One last point, as you may have noticed, Microsoft as well as other commercial vendors successfully fail at developing and providing adequate solutions for highly data-driven applications, so almost any software or framework you will encouter during this lecture or later, will be open-source and only be runnable on a UNIX-based operating system. Either you are already familiar with UNIX (lucky you), otherwise you will learn something valuable that will improve your life.\\

\setlength{\epigraphwidth}{0.9\textwidth}
\setlength\epigraphrule{0pt}
\epigraph{\itshape ``Microsoft is not the answer. Microsoft is the question. NO is the answer.''}{--- Erik Naggum \gtrsymDied~, \textit{Philantropist and Developer (Emacs, Lisp and SGML) }}


